Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-04-21 paper2020/paper.tex
kill 1st todo

\newif\ifanon\anontrue

@@

>>>>

\newif\ifanon\anonfalse

@@

Finally it would be desirable to improve automation of the system, and
evaluate it on a larger test set. As it stands Coq fully \emph{checks}
the proof of entailment for each (provable) problem. However, the
construction of such proofs has demanded human intervention. It would
be desirable to fully automate the proof construction step. For this
to make sense however we need a much larger test suite, properly
separated into a development and a (secret) test set. Otherwise, only
the limited power of the logic prevents us (or any followup work) to
fine-tune the rules of the system until one gets full coverage. This
kind of observation holds in general of any rule-based system, and
thus applies not only to the proof-construction phase, but also to the
underlying dynamic semantics and parsing phase (which is limited only
by the power of the language and frameworks used for its
implementation). In sum, contrary to statistical approaches to
language understanding, the value of the present work lies not in the
bare accuracy numbers which we are able to achieve, but in the details
of \emph{how} we do so: the of set of rules which we use, which is
described in detail here and in the work which we base ourselves upon
\citep{bernardy_computational_2020,bernardy_wide-coverage_2019}.
